Stage-Splitting a Modal Language

### 2014-08-05 paper/splitting.tex
first cut at splitting correctness theorem

You should think of these theorems as saying that 
splitting commutes with evaluation.

>>>>

\TODO what about totality of splitting?

%You should think of these theorems as saying that 
%splitting commutes with evaluation.
While these theorems are rather technical in nature, they imply that splitting a
program and running it is the same as using the semantics from
\ref{ssec:dynamics}.

For example, if we have some multi-stage function $f:A\to\fut(B\to C)~@~\bbone$,
then we expect \verb|prev{f a} b| will evaluate to the same value under our
staged dynamic semantics and when split.

Consider a term $\vdash e:\fut A~@~\bbone$ (like \verb|next{prev{f a} b}|) which
might contain computation at both stages. The correctness theorem here states
that:
\begin{theorem}
If $\vdash e:\fut A~@~\bbone$, then (by splitting)
\begin{itemize}
\item $\diaone [] e {\xi;v}$
\item $\dom \xi \vdash v \vsplito [v_1,v_2]$
\item $\reify \xi {v_2} q_S$
\item $q_S \mathbin{\tworedsym} v_S$
\end{itemize}
if and only if (by the staged dynamic semantics)
\begin{itemize}
\item $\diaone [] e {\xi;v}$
\item $\reify \xi v q_D$
\item $q_D \mathbin{\tworedsym} v_D$
\end{itemize}
and if so, then $v_S = v_D$.
\end{theorem}

\TODO why does splitting not show up in this theorem?
